Market-based Mechanisms for Resource Scheduling

### 2013-12-17 paper/paper.tex
Write a little bit more

Specifically, the auction tries to fit bids into the available resources in the
cluster as to maximize the amount of revenue from the auction. With each task
package, we associate a \emph{current price} in addition to the willingness to
pay; then the difference between the latter and the former is  the The agent
representing a framework's bid computes

>>>>

With each set of tasks, we associate a \emph{current price} in addition to the
willingness to pay; then the difference between the latter and the former is the
profit incurred by the framework for that set of tasks. The agent representing a
framework's bid initially sets the current price to equal a \emph{reserve price}
based on the amount of resources within the bid.

For the master, the goal of the auction is to pick a set of tasks to run which
is feasible (i.e., does not use resource beyond what is currently available) and
which maximizes the revenue (the sum of the \emph{current price} for each of the
tasks).

The auction operates by maintaining a set of winners, and asking each of
the frameworks' agents in turn to suggest a change to the set such that it
remains feasible and increases the master's revenue. The agent then takes an
action to maximize its represented framework's profit by putting as many tasks
as possible into the winning set. If the agent needs to evict some current
winners to make room for tasks that it wants to run, then it must raise the
current price of the tasks by an amount which exceeds the current price of the
evicted tasks; sometimes that may cause the current price to exceed the task's
willingness to pay, which indicates that there is too much competition driving
up the price to profitably run the task on the cluster at this time.

\subsection{Bidding policy}
Given a set of tasks it wishes to run, the framework must
